Untitled

### 2023-09-09 code/analysis_Redo.Rmd
ATT by mediators

splits <- c(-0.03, 0.1)

@@

did2s(
      data = df.profit %>% filter(!is.na(pc)) %>% mutate(pc = pc * 10 ), 
      yname = "Qcomp", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE) + I(Tx * pc) + I(Tx * pc^2),
        cluster_var = "STATE",
      verbose = FALSE
    )
```

>>>>

#splits <- c(-0.03, 0.1)

@@

did2s(
      data = df.profit %>% filter(!is.na(pc)) %>% mutate(pc = pc * 10 ), 
      yname = "Qcomp", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE) + I(Tx * pc) + I(Tx * pc^2) ,
        cluster_var = "STATE",
      verbose = FALSE
    )
```
